---
title: "A Tufte Handout Example"
runningheader: "Tufte Handout with R Markdown" # only for pdf output
subtitle: "An implementation in R Markdown" # only for html output
authors: "Raphael Lee, Javier Bolong, Allen Abel, Tricia Pulmano"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

[START HERE]

Intro

Hypothesis Testing

Hypothesis:

$H_0: \mu =  60$

$H_1: \mu > 60$

For this data set, we use a confidence interval of 95%.

Meaning, $\alpha=0.05$

We are testing this set of data on whether the amount of tires recycled on average, is more than 60 million tons.

Given this data, we should first look for the Population mean and Population variance.
These values will help us 
``` {r data, echo=FALSE}
library(readxl)
Tables <- read_excel("~/GitHub/Group-2-Third-Markdown-Project/Tables.xlsx")
Waste <- Tables$`Waste tire`
Recycled <- Tables$`Amount of recyled`
summary(Waste,Recycled)


plot(Waste, Recycled)

```
$\bar{x} = 94.55153448$

$\sigma^2 = 15,362.6468$


Then, we select 10 samples randomly and conduct a t-test on the sample selected

We select:

1. Denmark (38.0016)
2. Greece (30.0016)
3. Italy (354.0189)
4. Norway (31.011)
5. Czech Republic (45.0015)
6. Portugal (65.9988)
7. UK (394.9865)
8. Netherlands (61.9983)
9. Bulgaria (19.008)
10. Turkey (136.006)

Computing for Sample mean and standard deviation:
Sample Mean ($\bar{x}$)= 117.60322
Sample Standard Deviation = 139.613811


We use the equation:

$t = \frac{\bar{x}-\mu}{s/\sqrt{n}}$

Solving:
``` {r t-test, include=TRUE, echo=FALSE}
t <- (117.60322-60)/(139.613811/sqrt(10))
t
```

Then we compare the t value above to the value obtained in the t distribution with a confidence interval of 95%
``` {r tdistribution, include=TRUE, echo=FALSE}
u <- qt(c(0.95), df=9)
u
```
`r t` < `r u`

Because the t test value is less than the t distribution value, we fail to reject the null hypothesis.

Furthermore, if we find the p-value of the equation
``` {r pvalue, echo=FALSE}
p <- 1-pnorm(t)
p
```

The p-value is more than 0.05, therefore we fail to reject the null hypothesis.

`r p` > 0.05


