---
title: "A Tufte Handout Example"
runningheader: "Tufte Handout with R Markdown" # only for pdf output
subtitle: "An implementation in R Markdown" # only for html output
authors: "Raphael Lee, Javier Bolong, Allen Abel, Tricia Pulmano"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

[START HERE]

#Intro

#Parameters of Interest

The Parameter of interest is the claimed average total wasted recycled that is represented by μ

#Formulating the Null and Alternative Hypothesis

Knowing the parameter of interest, we can now formulate the hypothesis

The Null Hypothesis is represented by:
$H_0: \mu =  60$

While the Alternate Hypothesis is represented by:
$H_1: \mu > 60$

#Computation
We are testing this set of data on whether the amount of tires recycled on average, is more than 60 million tons.

First we have to look at the data given at the paper 

``` {r data, echo=FALSE}
library(readxl)
Tables <- read_excel("~/GitHub/Group-2-Third-Markdown-Project/Tables.xlsx")
Waste <- Tables$`Waste tire`
Recycled <- Tables$`Amount of recyled`
summary(Waste,Recycled)


plot(Waste, Recycled)

```

We can use the t-test which is represented by the equation due to it having less than 30 samples and no standard deviation given:

$t = \frac{\bar{x}-\mu}{s/\sqrt{n}}$


However given this data, we should first look and calculate for the Population mean and Population variance since its not given in the paper.

To look for these we can use these values to help us.

``` {r data, echo=FALSE}
library(readxl)
Tables <- read_excel("~/GitHub/Group-2-Third-Markdown-Project/Tables.xlsx")
Waste <- Tables$`Waste tire`
Recycled <- Tables$`Amount of recyled`
summary(Waste,Recycled)


plot(Waste, Recycled)

```
$\bar{x} = 94.55153448$

$\sigma^2 = 15,362.6468$

Furthermore since the significance is not also given, we decided to use a confidence interval of 95% for this data set.

Meaning, $\alpha=0.05$

Then, we select 10 samples randomly and conduct a t-test on the sample selected

Using a randomizer, we got the following samples from the paper:

1. Denmark (38.0016)
2. Greece (30.0016)
3. Italy (354.0189)
4. Norway (31.011)
5. Czech Republic (45.0015)
6. Portugal (65.9988)
7. UK (394.9865)
8. Netherlands (61.9983)
9. Bulgaria (19.008)
10. Turkey (136.006)

Using these 10 sample we can now compute for Sample mean and standard deviation that will be used for the t-test:
Sample Mean ($\bar{x}$)= 117.60322
Sample Standard Deviation = 139.613811

With all the needed value, we can now proceed to substitute them and solve the t-test using the following codes:

Solving for T:
``` {r t-test, include=TRUE, echo=FALSE}
t <- (117.60322-60)/(139.613811/sqrt(10))
t
```

Then we compare the t value above to the value obtained in the t distribution with a confidence interval of 95%
``` {r tdistribution, include=TRUE, echo=FALSE}
u <- qt(c(0.95), df=9)
u
```
`r t` < `r u`

#Discussion

The results gathered after hypothesis testing indicate that we fail to reject the null hypothesis stating that the mean amount of tires recycled is equal to 60 million tons. Since the global amount of tire waste is estimated to range from 60 to 80 million tons, it means that there are more tires being wasted than those being recycled. This can be attributed to the fact that even though there are few European countries able to fully recycle tires, the total amount of tires they generate is significantly lower than those countries unable to recycle all their tires. For instance, even though Denmark has a tire recycling rate of 97%, since their number of tires is only 39 million tons, the amount of recycled tires will be unable to match the tire waste from Turkey which has 260 million tons of tires while only having 52% recycling rate.

This newfound information tells us that the tire recycling program has to be improved especially in countries generating a large amount of tires in order for the program to make significant effects in improving the environmental situation in Europe. Those countries with lower tire recycling rates can try to follow the tire recycling strategies of those countries with high recycling rates.


#Conclusion 
 
After comparing the  t value above to the value obtained in the t distribution with a confidence interval of 95% we concluded that we fail to reject the null hypothesis due to the  that the t test value is less than the t distribution value

Furthermore, if we can also find the p-value of the equation
``` {r pvalue, echo=FALSE}
p <- 1-pnorm(t)
p
```

Since we got a p-value that is more than 0.05, it supported the evidence to fail to reject the null hypothesis.

`r p` > 0.05



 

